---
title: "ReadMe"
author: Colin Millar
date: 21th December 2016
output:
  md_document:
    variant: markdown_github
    toc: true
    toc_depth: 2
---

[![Build Status](https://travis-ci.org/Faskally/loggercal.svg?branch=master)](https://travis-ci.org/Faskally/loggercal)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(loggercal)
```

# Temperature Logger Calibration


The first step is to load the loggercal package

```{r library, echo=TRUE, eval=FALSE}
devtools::install_github("faskally/loggercal")
library(loggercal)
```

The first thing to do is to set the location of the external and internal calibrations we are
looking to compare.

```{r input}
externalCalDir <- "data-raw/External Calibrations/"
internalCalDir <- "data-raw/100214/"
```

## External calibration data

Next we look for the external calibration files from a UKAS calibration.  These should all be in one directory.
In this case we find two external calibrations.  These are read in using the `loggercal` function
`readExternalCal`

```{r read_ukas}
ukas <- readExternalCal(externalCalDir)
str(ukas)
```

we now fit a model to the external calibration data

```{r external_model}
externalCalMod <- lapply(ukas $ data, function(x) lm(cal ~ poly(control, 2), data = x[-1,]))
```

## Read in internal calibration data

```{r internal_calibration}
internalCal <- readInternalCal(internalCalDir)
internalCal
```

Now it should be checked that the external calibration loggers were included in the experiment

```{r check_logger}
ukas
```

And here, the last two loggers in the internal calibration are the externally calibrated ones.  The
next step is to define the start and stop of the calibration.  This can be done manually (note that
the value `startStopSec` is in seconds, while the plot axis is in minutes, so you need to multiply
by 60 to set limits in secs):

```{r trim_manual}
plot(internalCal)
internalCal$startStopSec <- c(100,9900) * 60
plot(internalCal)
```

Or this can be done using a graphical approach, in a handy function.

```{r trim_graphical, eval = FALSE}
internalCal <- findStartSec(internalCal)
internalCal <- findStopSec(internalCal)
plot(internalCal)
```

## run the calibration

The function `calibration` runs the full calibration method.  Here, as we are running an example,
we only use 5 simulations to back calculate the logger error.  Normally a large number like 99 or
999 should be used, but this can take up to a day to run.

```{r run calibration}
cal <- calibration(internalCal, externalCalMod, n = 5)
```

Once the calibration simulations have completed, the coefficients from the calibrations are
extracted and tabled (e.g. for import into a logger database with calibration functionality).

```{r table_coefficients}
coefs <- getCoefs(cal)
tabCoefs <- tableCoefs(coefs, cal = internalCal)
tabCoefs
```


## A full analysis script

```{r full_analysis, eval = FALSE}
library(loggercal)

externalCalDir <- "data-raw/External Calibrations/"
internalCalDir <- "data-raw/100214/"

# external calibration -------------------------

# read in external calibrations
ukas <- readExternalCal(externalCalDir)

# fit a model to the external calibration data
externalCalMod <- lapply(ukas $ data, function(x) lm(cal ~ poly(control, 2), data = x[-1,]))

# internal calibration -------------------------

# read in internal calibration experiment
internalCal <- readInternalCal(internalCalDir)

# trim off ends
internalCal$startStopSec <- c(100,9900) * 60

# plot to check
plot(internalCal)

# perform a calibration ------------

cal <- calibration(internalCal, externalCalMod, n = 5)

# convert coefficients to non orthogonal polynomials
coefs <- getCoefs(cal)
tabCoefs <- tableCoefs(coefs, cal = internalCal)

write.csv(file = file.path(file.path(internalCalDir), "coefficients.csv"), tabCoefs, row.names = FALSE)

# Done -----------------
```
