---
title: "ReadMe"
author: Colin Millar
date: 21th December 2016
output:
  md_document:
    variant: markdown_github
---

[![Build Status](https://travis-ci.org/Faskally/loggercal.svg?branch=master)](https://travis-ci.org/Faskally/loggercal)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(loggercal)
```

# Temperature Logger Calibration


The first step is to load the loggercal package

```{r library, echo=TRUE, eval=FALSE}
devtools::install_github("faskally/loggercal")
library(loggercal)
```

The first thing to do is to set the location of the external and internal calibrations we are
looking to compare.

```{r input}
externalCalDir <- "data-raw/External Calibrations/"
internalCalDir <- "data-raw/100214/"
```

## External calibration data

Next we look for the external calibration files from a UKAS calibration.  These should all be in one directory.
In this case we find two external calibrations.  These are read in using the `loggercal` function
`readExternalCal`

```{r read_ukas}
ukas <- readExternalCal(externalCalDir)
str(ukas)
```

we now fit a model to the external calibration data

```{r external_model}
externalCalMod <- lapply(ukas $ data, function(x) lm(cal ~ poly(control, 2), data = x[-1,]))
```

## Read in internal calibration data

```{r internal_calibration}
internalCal <- readInternalCal(internalCalDir)
internalCal
```

Now it should be checked that the external calibration loggers were included in the experiment

```{r check_logger}
ukas
```

And here, the last two loggers in the internal calibration are the externally calibrated ones.  The
next step is to define the start and stop of the calibration.  This can be done manually (note that
the value `startStopSec` is in seconds, while the plot axis is in minutes, so you need to multiply
by 60 to set limits in secs):

```{r trim_manual}
plot(internalCal)
internalCal$startStopSec <- c(100,9900) * 60
plot(internalCal)
```

Or this can be done using a graphical approach, in a handy function.

```{r trim_graphical, eval = FALSE}
internalCal <- findStartSec(internalCal)
internalCal <- findStopSec(internalCal)
plot(internalCal)
```
