---
title: "ReadMe"
author: Colin Millar
date: 21th December 2016
output:
  md_document:
    variant: markdown_github
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(loggercal)
```

# Temperature Logger Calibration

## Quick example

The first step is to load the loggercal package

```{r library, echo=TRUE, eval=FALSE}
devtools::install_github("faskally/loggercal")
library(loggercal)
```

Next we look for the external calibration files from a UKAS calibration.  These are normally to be
found in a folder called "External Calibrations", but if you are working from within the package directory
(as this readme file is) the you will have to look in "data-raw/External Calibration".

```{r input}
externalCalDir <- "data-raw/External Calibrations/"
externalCalFiles <- list.files(externalCalDir, full.names = TRUE)
```

In this case we find two external calibrations.  This is read in using the `loggercal` function
`readExternalCal`

```{r read_ukas}
ukas <- readExternalCal(externalCalFiles)
```

we now fit a model to the external calibration data

```{r external_model}
externalCalMod <- lapply(ukas $ data, function(x) lm(cal ~ poly(control, 2), data = x[-1,]))
```




